A generalized definition of multidimensional item response theory parameters

### 2023-02-03 output/paper_draft/paper_M2PLM_parameters.Rmd
Finishes including example in Tezza et al., 2018

```{r set-cov-matrix-Tezza2018}
# See Tezza et al., 2018, p. 927:
# > No presente estudo, a correlação entre a dimensão 1 e a dimensão 4
# > foi de aproximadamente 0,4.
COV_MATRIX_VALUE <- diag(4)
COV_MATRIX_VALUE[1, 4] <- COV_MATRIX_VALUE[4, 1] <- .4
```

@@

>>>>

### @tezza_modelo_2018

```{r set-cov-matrix-Tezza2018}
# See Tezza et al., 2018, p. 927:
# > No presente estudo, a correlação entre a dimensão 1 e a dimensão 4
# > foi de aproximadamente 0,4.
COV_MATRIX_VALUE <- diag(4)
DIMS_CORR        <- .4
COV_MATRIX_VALUE[1, 4] <- COV_MATRIX_VALUE[4, 1] <- DIMS_CORR
```

@@

@tezza_modelo_2018 provide us with another example that allows showcasing
the effect of correlated dimensions on negative discrimination parameters.
In their model, dimensions 1 and 4 are estimated to have a correlation of
`r DIMS_CORR`.
With such latent space structure, items that strongly discriminate in any or
both of these two dimensions change drastically their multidimensional
parameters from the agnostic to the covariance-based version
(see Table \@ref(tab:empirical-table-Tezza2018-out)) ---this happens,
for example, with items 57 and 60. These items also have different-sign
discrimination parameters in dimensions 1 and 4, so their situation is
similar to items 2 and 3 in Table \@ref(tab:example-items-table-out) and
Figure \@ref(fig:item-plot-out),
thus the decrease in their $`r MDISC_ITEM`$ parameter.
The effect on the direction is also patent in the angles these items make with
these dimensions, which change up to almost 20º, compared with at most 7º in the
other two dimensions, and around 1º in most cases.

On the other hand, in cases such as items 12 or 59, which have
relatively low discrimination parameters on those two dimensions
(compared with the ones in dimension 2 and 3, respectively) are barely affected.
In these cases, we also notice that the angles are barely affected.
The most extreme change in these two examples occurs in
the direction of item 12 with respect to dimension 4. We see how the large
discrimination in dimension 1, when combined with the correlation
with dimension 4, induces a decrease in the angular direction
with that dimension.
In this case, being the discrimination in dimension 4 so low, the situation is
very similar to item 4 in Table \@ref(tab:example-items-table-out)
and Figure \@ref(fig:item-plot-out).
